%-*-latex-*-
\mychapter{101}{4000}{Asymptotics and algorithmic runtime analysis}

Open \verb!algorithm-analysis-how-fast-is-an-algorithm.tex!
and you'll see
\[
\verb!\input{exercises/runtime-of-sum-of-squares/main.tex}!
\]
Goto \verb!exercises/runtime-of-sum-of-squares/! and in that directory you'll
see \verb!question.tex! and \verb!answer.tex!.
\verb!question.tex! contains the question
and
\verb!answer.tex! contains the answer.
Near the top of \verb!answer.tex!, you'll see
\[
\textsc{Author: John Doe. Datetime: 2024-11-12 09:00:00}
\]

For the question you are working on, imitate the above example,
replacing John Doe with your name and datetime with the date and time
you are done.

To include your exercise, start by placing it in the
\verb!exercises! directory. For example, if your exercise
directory is named \verb!tree-6!, you should see the
following output when running \verb!ls! inside the
\verb!exercises! directory:

\begin{Verbatim}[frame=single, fontsize=\small]
runtime-of-sum-of-squares  tree-6
\end{Verbatim}

Next, to display the exercise in this document, from the main directory open:
\[
\verb!algorithm-analysis-how-fast-is-an-algorithm.tex!
\]
then locate the placeholder:
\[
\verb!%???%!
\]
and replace it with:

\[
\verb!\input{exercises/tree-6/main.tex}!
\]

%???%

Now, go back to the main directory and run the \verb!make! command.
This should compile the document with your exercise included.

To add your answer, navigate to the directory of your exercise and
enter your solution in the file named \verb!answer.tex!. Return to
the main directory, run \verb!make! again, and your solution should
appear on the following pages of this document.

To properly generate the table of contents you'll need to run make twice.
If you see some errors involving missing python code, let me know.

Once you are done, send me the directory of the exercise, tar'd and gzipped.
It should be a directory with \verb!main.tex!, \verb!question.tex! and
\verb!answer.tex!.
Retain the original directory name. 
For instance it might be
\[
\verb!runtime-of-sum-of-squares.tar.gz!
\]
You'll also need to tell me chapter and course.

\newpage\input{algorithm-analysis-how-fast-is-an-algorithm.tex}

\begin{python0}
from solutions import *
prepare_solutions()
\end{python0}
\input{solutions.tex}
\begin{python0}
from solutions import *
clear()
\end{python0}

